\cvsection{Experience}

\begin{cventries}

 \cventry {Software Engineer ~~~·~~~ Go,  Ruby,  Puppet,  Ansible, Terraform}
  {\href{https://stripe.com}{Stripe \faExternalLink}} {Seattle WA,
    USA} {May 2021 - present} {
    \begin{cvitems}
    \item Building infrastructure for Stripe's PCI-compliant cardholder data environment,
    with a focus on improving system security, reliability, and developer productivity.
    \item Product security lead of three infrastructure teams.
    \end{cvitems}
  }

 \cventry {Software Engineer ~~~·~~~ Java, C\#, Unity}
  {\href{https://www.tier9studios.com}{Tier 9 Game Studios \faExternalLink}} {Waterloo ON,
    Canada} {May - Aug 2020} {
    \begin{cvitems}
    \item Architected a framework for efficiently fetching,  caching, and rendering unbounded tile-based maps in Unity.
    \item Built foundational libraries to provide database entity management,  asynchronous REST and Websocket requests, and multi-server synchronization.
    \item Implemented real-time multiplayer game mechanics using Websockets.
    \item Introduced asynchronous programming, dependency injection, and other industry-standard methodologies.
    \item Contributed many quality-of-life improvements to deployment and migration procedures.
    \end{cvitems}
  }

 \cventry {Software Engineer Intern ~~~·~~~ Scala, Ruby, React}
  {\href{https://stripe.com}{Stripe \faExternalLink}} {Seattle WA,
    USA} {Jan - April 2020} {
    \begin{cvitems}
    \item Member of Revenue Products team, working primarily on the Billing Analytics event pipeline.
	\item Wrote large scale Apache Spark jobs in Scala to aggregate events, rank products, and produce time-series aggregations of historical data.
	\item Designed and implemented new Billing Analytics charts using React and Ruby.
	\item Refactored event processing pipeline to make event aggregation jobs idempotent, resulting in more consistent (and easier to test) behaviour.
	\item Wrote a suite of Apache Spark queries to identify and fix inconsistencies in user facing data.
    \end{cvitems}
  }

  \cventry {Software Engineer Intern ~~~·~~~ C, C++, Java}
  {\href{https://www.yugabyte.com}{YugaByte \faExternalLink}} {Sunnyvale CA,
    USA} {May - Aug 2019} {
    \begin{cvitems}
    \item Member of Query Layer team, working to integrate Postgres fronted with
      distributed document store backend.
    \item Wrote robust and portable shared memory library to improve system
      catalog cache consistency across nodes.
    \item Added support for Postgres role-based access control, ensuring
      consistency in a distributed environment.
    \item Designed and implemented a gflag-based configuration mechanism to make
      Postgres configurable through YugaByte. \nres{\item Added support for
        various \textit{ALTER TABLE} variants in Postgres.} \nres{\item
        Refactored post-test cleanup process to reduce flakiness and increase
        test speed.}
    \item Contributor on multiple open-source projects at YugaByte, including
      \thinspace
      \href{https://github.com/YugaByte/yugabyte-db/commits?author=srhickma}{\color[HTML]{3090C7}{yugabyte-db
          \faExternalLink}}.
    \end{cvitems}
  }

  \cventry {Software Engineer Intern ~~~·~~~ Java, Kotlin}
  {\href{https://www.faire.com}{Faire \faExternalLink}} {Kitchener ON, Canada}
  {Sept - Dec 2018} {
    \begin{cvitems}
    \item Architected an inter-server event framework using Amazon Kinesis and
      Protocol Buffers.
    \item Designed and implemented APIs to support offline ordering,
      retailer-to-maker referrals, and out-of-stock products, contributing to
      user acquisition and an overall increase in sales.
    \item Implemented several complex email cadences to promote and notify users
      of new features, with visualized A/B tests for subject lines and content.
      \nres{\item Added web-hooks to push logged errors into Redshift,
        supporting more complex error analysis.} \nres{\item Mentored and
        on-boarded new backend developers as the team nearly doubled in size.}
    \item Integrated code coverage tracking into TravisCI to motivate better
      testing practices.
    \end{cvitems}
  }
    
  \cventry {Software Developer Intern ~~~·~~~ Go, C\#}
  {\href{https://spatial.is}{Spatial \faExternalLink}} {New York NY, USA} {Jan -
    April 2018} {
    \begin{cvitems}
    \item Proposed and implemented a scalable and load-balanced backend
      architecture for user-management, real-time messaging, and data
      synchronization on AWS, written in Go.
    \item Introduced stateless authentication and role-based authorization
      mechanism using JSON Web Tokens.
    \item Developed platform agnostic .NET web socket and http implementations
      for multi-threaded API clients. \nres{\item Wrote memory efficient Google
        Poly wrapper to rank and page results based on keywords.}
    \item Added DevOps functionality through metrics gathering (Prometheus +
      Grafana), and deployment scripts (Ansible) for all servers.
    \end{cvitems}
  }
    
  \cventry {Software Developer Intern ~~~·~~~ Java}
  {\href{https://miovision.com}{Miovision \faExternalLink}} {Kitchener ON,
    Canada} {May - Aug 2017} {
    \begin{cvitems}
    \item Designed and implemented a performant API to export large amounts of data
      from Hibernate + MySQL to AWS.
    \item Refactored data extraction workflow to parallelize tasks, increase
      accuracy, and pave the way for future cost savings initiatives.
    \item Deployed metrics agents to monitor download speeds and cache
      performance of satellite servers. \nres{\item Wrote and maintained POJOs
        to facilitate json data transfer to and from computer vision software.}
      \nres{\item Worked closely with computer vision team to determine
        specifications and integration details of new software and the data
        export API.}
    \end{cvitems}
  }

\end{cventries}
