\cvsection{Projects}

\begin{cventries}
  
  \cventry {Secure nonce file transfers in the cloud}
  {\href{https://github.com/srhickma/dead-drop}{dead-drop \faExternalLink}} {Go}
  {May 2019 - present} {
    \begin{cvitems}
    \item Created tool for securely transferring files via an untrusted
      middle-man server.
    \item Utilized AES-CTR with HMAC to encrypt and authenticate user data on
      the client side.
    \item Implemented client-server authentication using asymetric key
      cryptography and Json Web Tokens.
    \end{cvitems}
  }
  
  \cventry {Fast and Automatic Formatter of Context-Free Languages}
  {\href{https://github.com/srhickma/padd}{padd \faExternalLink}} {Rust} {March
    2018 - present} {
    \begin{cvitems}
    \item Wrote library to efficiently format text using a CFG and a set of
      patterns.
    \item Implemented multi-threaded cli wrapper to batch-format projects
      (directories) using diff tracking.
    \item Created a specification language for generating lexers and parsers at
      runtime.
    \end{cvitems}
  }

  \nres{\cventry {2D procedural side-scroller using Unity Game Engine}
    {\href{https://github.com/srhickma/to\_be\_discovered}{to\_be\_discovered
        \faExternalLink}} {C\#} {2017} {
      \begin{cvitems}
      \item Wrote scalable node-based pathfinding algorithm capable of
        supporting hundreds of concurrent agents.
      \item Created performant data structures as a powerful base for bounded
        random generation.
      \end{cvitems}
    }}
  
  \nres{\cventry {Text-based process manager for boosting productivity}
    {\href{https://github.com/srhickma/lens}{lens \faExternalLink}} {Java}
    {2017} {
      \begin{cvitems}
      \item Modified and embedded open source JetBrains terminal emulator
        JediTerm into the core application.
      \item Created a command framework for executing various local processes
        through a terminal prompt.
      \end{cvitems}
    }}
  
  \nres{\cventry {Database for sharing study resources}
    {\href{www.photesto.space}{www.photesto.space \faExternalLink}} {PHP, Java,
      MySQL} {2015-2016} {
      \begin{cvitems}
      \item Created login system with encryption and email verification to
        protect user data.
      \item Styled website responsively for optimal performance on both desktop
        and mobile devices.
      \end{cvitems}
    }}
  
\end{cventries}
